Learning From Massive Noisy Labeled Data for Visual Classification

### 2014-11-14 paper.tex
Final

%%%%%%%%% ABSTRACT
\begin{abstract}
Large-scale strongly supervised datasets are crucial to train deep neural networks for various computer vision problems. Obtaining such well labeled data is usually expensive, but collecting web data with noisy labels is much more effortless. In this paper we model label noise with a graphical model and further integrate it into a deep learning framework. Experiments are conducted on a collected large-scale web dataset. The results show that noisy labeled data benefit the training of deep neural networks, and exploiting our label noise model can further improve the performance.
\end{abstract}

@@

{\bf Direct learning with noisy labels:} Among other consequences, many works have shown that noise can adversely impact the classification performances of induced classifiers \cite{zhu2004class}. 
Experiments in the literature show that the performances of classifiers inferred by label noise-robust algo- rithms are still affected by label noise. Label noise-robust methods seem to be adequate only for simple cases of label noise that can be safely managed by overfitting avoidance \cite{frenay2013classification}.

{\bf Semi-supervised learning:} Apart from modeling label noise explicitly, some semi-supervised learning algorithms are developed to utilize weakly labeled or even unlabeled data. Label Propagation method \cite{zhu2002learning} explicitly uses ground truths of well-labeled data to classify unlabeled samples. However, it suffers from computing pairwise distance, which has quadratic complexity with the number of data samples and cannot be applied on largescale datasets. Weston et al. \cite{weston2012deep} proposed to embed a pairwise loss in the middle layer of a deep neural net- work, which benefits the learning of discriminative features. But they need extra information about whether a pair of unlabeled images belong to same class, which cannot be obtained in our problem.

{\bf Transfer learning:} The success of Convolutional Neural Networks (CNNs) lies in their capability of learning rich and hierarchical image features. However, the model parameters cannot be properly learned when training data is not enough. Researchers proposed to conquer this problem by first initializing the CNN parameters with a model pretrained on a larger yet related dataset, and then finetuning the CNN on the smaller dataset of specific task \cite{krizhevsky2012imagenet, oquab2013learning, azizpour2014generic}. Nevertheless, this kind of transfer learning scheme could be suboptimal when the two tasks are just loosely related. In our case of clothes recognition, we show that training a deep model directly with massive weakly label data achieves bette performance compared with finetuning from a ImageNet pretrained model.

@@

We estimate $\mat{C}$ on a relatively small dataset $\mathcal{D}_c = \{(\vec{x},\vec{y},\tilde{\vec{y}})\}_N$, where we have $N$ images with both clean and noisy label. As prior information about $\vec{z}$ is not available, we just solve the following optimization problem:
\begin{equation}
    \max_{\mat{C},\vec{z}^{(1)},\cdots,\vec{z}^{(N)}} \sum_{i=1}^N \log p(\tilde{\vec{y}}^{(N)}|\vec{y}^{(N)},\vec{z}^{(N)})
\end{equation}
Obviously, sample $i$ contributes nothing to the optimal $\mat{C}^*$ if $\vec{y}^{(i)}$ and $\tilde{\vec{y}}^{(i)}$ are equal. So that we ignore those samples and reinterpret the problem in another form by exploiting Eq~\ref{eq:likelihood}:
\begin{equation}
\begin{aligned}
\max_{\mat{C},\vec{t}} \quad & E=\sum_{i=1}^{N'} \log \alpha^{\vec{t}_i} + \log (\tilde{\vec{y}}^{(i)T} \mat{C} \vec{y}^{(i)})^{1-\vec{t}_i}\\
\text{subject to} \quad & \mat{C} \text{ is a stochastic matrix of size } L\times L \\
                    & \vec{t} \in \{0,1\}^{N'}
\end{aligned}
\end{equation}
where $\alpha=\frac{1}{L-1}$ and $N'$ is the number of remaining samples. The semantic meaning of the above formulation is that we need to assign each $(\vec{y},\tilde{\vec{y}})$ pair the optimal noise type, while finding the optimal $\mat{C}$ simultaneously.

>>>>

%%%%%%%%% ABSTRACT
\begin{abstract}
Large-scale supervised datasets are crucial to train deep neural networks for various computer vision problems. However, obtaining a massive amount of well labeled data is usually very expensive and time consuming. In this paper, we introduce a general framework to train deep nets with only limited number of clean labels and millions of easily obtained noisy labels. We model label noises with a graphical probabilistic framework and further integrate it into the deep learning system. To demonstrate the performance of our approach, we collect a large scale clothing classification dataset with both noisy and clean labels. We demonstrate the effectiveness of our approach on this dataset, showing the possibility of learning a strong deep model with only a small amount of clean labels.
\end{abstract}

@@

{\bf Direct learning with noisy labels:} Among other consequences, many works have shown that noise can adversely impact the classification performances of induced classifiers \cite{zhu2004class}. 
Experiments in the literature show that the performances of classifiers inferred by label noise-robust algorithms are still affected by label noise. Label noise-robust methods seem to be adequate only for simple cases of label noise that can be safely managed by overfitting avoidance \cite{frenay2013classification}.

{\bf Semi-supervised learning:} Apart from modeling label noise explicitly, some semi-supervised learning algorithms are developed to utilize weakly labeled or even unlabeled data. Label Propagation method \cite{zhu2002learning} explicitly uses ground truths of well-labeled data to classify unlabeled samples. However, it suffers from computing pairwise distance, which has quadratic complexity with the number of data samples and cannot be applied on largescale datasets. Weston et al. \cite{weston2012deep} proposed to embed a pairwise loss in the middle layer of a deep neural network, which benefits the learning of discriminative features. But they need extra information about whether a pair of unlabeled images belong to same class, which cannot be obtained in our problem.

{\bf Transfer learning:} The success of Convolutional Neural Networks (CNNs) lies in their capability of learning rich and hierarchical image features. However, the model parameters cannot be properly learned when training data is not enough. Researchers proposed to conquer this problem by first initializing the CNN parameters with a model pretrained on a larger yet related dataset, and then finetuning the CNN on the smaller dataset of specific task \cite{krizhevsky2012imagenet, oquab2013learning, azizpour2014generic}. Nevertheless, this kind of transfer learning scheme could be suboptimal when the two tasks are just loosely related. In our case of clothes recognition, we show that training a deep model directly with massive weakly label data achieves better performance compared with finetuning from a ImageNet pretrained model.

@@

We estimate $\mat{C}$ on a relatively small dataset $\mathcal{D}_c = \{(\vec{x},\vec{y},\tilde{\vec{y}})\}_N$, where we have $N$ images with both clean and noisy label. As prior information about $\vec{z}$ is not available, we just solve the following optimization problem:
\begin{equation}
    \max_{\mat{C},\vec{z}^{(1)},\cdots,\vec{z}^{(N)}} \sum_{i=1}^N \log p(\tilde{\vec{y}}^{(i)}|\vec{y}^{(i)},\vec{z}^{(i)})
\end{equation}
Obviously, sample $i$ contributes nothing to the optimal $\mat{C}^*$ if $\vec{y}^{(i)}$ and $\tilde{\vec{y}}^{(i)}$ are equal. So that we ignore those samples and reinterpret the problem in another form by exploiting Eq~\ref{eq:likelihood}:
\begin{equation}
\begin{aligned}
\max_{\mat{C},\vec{t}} \quad & E=\sum_{i=1}^{N'} \log \alpha^{\vec{t}_i} + \log (\tilde{\vec{y}}^{(i)T} \mat{C} \vec{y}^{(i)})^{1-\vec{t}_i}\\
\text{subject to} \quad & \mat{C} \text{ is a stochastic matrix of size } L\times L \\
                    & \vec{t} \in \{0,1\}^{N'}
\end{aligned}
\end{equation}
where $\alpha=\frac{1}{L-1}$ and $N'$ is the number of remaining samples. The semantic meaning of the above formulation is that we need to assign each $(\vec{y},\tilde{\vec{y}})$ pair the optimal noise type, while finding the optimal $\mat{C}$ simultaneously.
